Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Add a conflict resolution example of verbal vs. visual learning style

Other rule groups may invoke random selection, select between stories
based on child preferences or curriculum, or (during development) flag
an error to highlight an unexpected ambiguity.

>>>>

Other rule groups may invoke random selection, select between stories
based on child preferences or curriculum (for example, the system
could attempt to learn a child's preference for verbal vs. visual
learning), or (during development) flag an error to highlight an
unexpected ambiguity.
